---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  comment   = "#>",
  # fig.path = "man/figures/README-",
  out.width = "100%",
  warning   = FALSE,
  message   = FALSE
)
library(rmarkdown)
library(knitr)
```

# **Oyster Resource Suitability Model**
The purpose of this repository is to process and model Coastal Master Plan data to aid the ***Coastal Protection and Restoration Authority’s (CPRA) efforts to  recover, manage, and maximize eastern oyster (Crassostrea virginica) resources*

<br>

# Packages used in analysis data
```{r}
library(tidyverse)
library(sf)
library(sp)
library(raster)
library(rgdal)
library(mapview)
library(waver)
library(logger)
```

# Installation
```{r, eval = FALSE }
install.packages(c("tidyverse", "sf", "sp", "raster",     # if missing packages
                   "rgdal", "mapview", "waver", "logger")) 
```

# Steps to get data outputs:
The final data outputs from the AOC and Traditional cultch models are located in `/data` folder. Additionally, all of the raw data used to generate the AOC and traditional cultch model data are packaged in this repository, allowing anyone to run the same analysis from there machine. 

## Preprocessing 
1. If necessary, **install the above packages to successfully run** the scripts in this projects
2. Open `cpra_orz/mp/process_mp.R` and run the entire script, this script will grid the MP datasets to the MP grid, and then rasterize the grid to a raster stack.
3. Open `cpra_orz/shapes/landwater.R` and run the entire script, this script create a 3 rasters (binary landwater, only land, only water) and 1 land polygon. These files are saved to `cpra_orz/data/masks`, and are used going forward to mask out land areas.

<br>

## AOC model
1. Open `cpra_orz/aoc/depth.R` and run the entire script
2. Open `cpra_orz/aoc/roads.R` and run the entire script
3. Open `cpra_orz/aoc/sediment_dep.R` and run the entire script
4. Open `cpra_orz/aoc/fetch.R` and run the entire script 
  - ***(This script will take >5 hours to fully run, I don't recommend running this script unless you wish to get an entirely new fetch dataset, otherwise, the necessary fetch data can be found in `data/fetch/`)***
5. Open `cpra_orz/aoc/commercial_viability.R` and run the entire script
6. Open `cpra_orz/aoc/oyster_viability.R` and run the entire script
7. Open `cpra_orz/aoc/aoc.R` and run the entire script, AOC model outputs have now been saved to `cpra_orz/data/aoc`

<br>

## Traditional cultch model
1. Open `cpra_orz/traditional_cultch/traditional_cultch.R` and run the entire script, Traditional cultch model outputs have now been saved to `cpra_orz/data/traditional_cultch`

<br>

## Masks + Reference layers
1. Open `cpra_orz/shapes/oyster_harvest_areas.R` and run the entire script, this script create a raster of LDH Oyster harvest classification areas for masking
2. Open `cpra_orz/shapes/coastal_use_permits.R` and run the entire script, this script create a raster of Coastal use permits for masking
3. Open `cpra_orz/shapes/navigation_channels` and run the entire script, this script create a raster of navigation channels for masking
4. Open `cpra_orz/shapes/state_owned_water_bottoms.R` and run the entire script, this script creates a raster state owned water bottoms
5. Open `cpra_orz/shapes/cpra_projects.R` and run the entire script, this script creates a raster of CPRA Restoration projects for masking




```{r}

```

